---
title: "Shakespeare"
author: "Ben Schmidt"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r, fig.show='hold'}
library(TEIdy)
tree = xml2::read_xml("https://raw.githubusercontent.com/textcreationpartnership/A50919/master/A50919.xml")


library(dplyr)
node = tree %>% xpl(2) %>% xpl(2) %>% xpl(1)
all = node %>% TEIdy::TEIdy(discard = c("teiHeader"), ignore = c("text")) %>% as_data_frame
all %>% summarize_all(~is.na(.) %>% sum )
node %>% TEIdy::TEIdy(mode="summary")
?summarize_all

by_species <- iris %>% group_by(Species)
by_species %>% mutate_all(funs(inches = . / 2.54))



```


```{r}
library(stringr)
library(tidytext)
all %>% unnest_tokens(word, text) %>% group_by(`div-n`) %>% mutate(word2 = lead(word, 1)) %>%
  filter(!is.na(`div-n`)) %>% transmute(bigram = paste(word, word2), div = `div-n`) %>%
  group_by(div, bigram) %>% summarize(count=n()) %>%
  tidytext::bind_tf_idf(bigram, div, count) %>%
  arrange(-tf_idf) -> data

data %>% group_by(div) %>% slice(1:3) %>% arrange(div)

library(ggplot2)
d = all %>% group_by(`act-n`, `scene-n`, `sp-who`) %>% summarize(count=n()) %>% group_by(`sp-who`) %>% mutate(total = sum(count)) 

d %>%
  filter(total > 100) %>% ggplot() + aes(y=`act-n`, x = `scene-n`, size = count) + geom_point(data = d %>% group_by(`act-n`, `scene-n`) %>% summarize(count = sum(count)), alpha = 0.2) + geom_point() + facet_wrap(~`sp-who`) + scale_size_continuous(trans='sqrt')
  

library(TEIdy)
acts = d %>% TEIdy(discard = c("w", "c"))
acts
```


```{r}
act1 %>% unnest_tokens(word, text) %>% group_by(`sp-who`) %>% summarize(count=n())

header = tree %>% xpl(1) %>% to_frame

colnas = . %>% apply(., 2, function(col) sum(is.na(col))) %>% order

reselect = function(frame) { neworder = frame %>% colnas; frame[neworder] }

header %>% filter(!is.na(`sex-value`)) %>% reselect()


macbeth = tree %>% to_frame

library(tidytext)
framed = d %>% to_frame %>% unnest_tokens(word, text)

library(ggplot2)
framed %>%
  group_by(stage, word) %>%
  summarize(count=n()) %>%
  arrange(-count) %>%
  ggplot() + geom_bar(aes(x=word, y = count, fill=stage), position="dodge", stat="identity") + coord_flip() +
  facet_wrap(~stage)


```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
