---
title: "Milton"
author: "Ben Schmidt"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Reading Paradise Lost from the EEBO version, and looking for the most distinguishing words in each book.

```{r, fig.show='hold'}
library(TEIdytext)
library(tidytext)
fname = system.file("extdata", "ParadiseLost.xml", package="TEIdytext")
data = TEIdy(fname)

data %>% select(plaintext, div.book.n) %>% 
  unnest_tokens(word, plaintext) %>% 
  mutate(div.book.n = as.numeric(div.book.n)) %>%
  group_by(div.book.n, word) %>% 
  summarize(count=n()) %>% 
  bind_tf_idf(word, div.book.n, count) %>%
  arrange(div.book.n, -tf_idf) %>%
  slice(1:6) %>%
  ggplot() + geom_point(aes(x=div.book.n, y=word, size=count)) + 
  scale_size_continuous(trans='sqrt') + facet_wrap(~div.book.n, scales='free_y')

```


```{r}
data %>% filter(!is.na(author))
```


```{r}
act1 %>% unnest_tokens(word, text) %>% group_by(`sp-who`) %>% summarize(count=n())

header = tree %>% xpl(1) %>% to_frame

colnas = . %>% apply(., 2, function(col) sum(is.na(col))) %>% order

reselect = function(frame) { neworder = frame %>% colnas; frame[neworder] }

header %>% filter(!is.na(`sex-value`)) %>% reselect()


macbeth = tree %>% to_frame

library(tidytext)
framed = d %>% to_frame %>% unnest_tokens(word, text)

library(ggplot2)
framed %>%
  group_by(stage, word) %>%
  summarize(count=n()) %>%
  arrange(-count) %>%
  ggplot() + geom_bar(aes(x=word, y = count, fill=stage), position="dodge", stat="identity") + coord_flip() +
  facet_wrap(~stage)


```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
